%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
  {Freelance Software Developer \& Consultant}
  {Self-Employed}
  {remote and Hamburg, Germany}
  {Jul. 2012 - PRESENT}
  {
    \begin{cvitems}
      \item {I worked project-based for different Clients and}
      \item {implemented web applications, online-shops, modern single page application and web/hybrid/native mobile applications together with agencies and}
      \item {I were also hired by agencies to develop their software architecture.}
    \end{cvitems}
  }
\cventry
  {Project Lead Frontend Development}
  {ABOUT YOU GmbH (e-commerce startup by OTTO Group)}
  {Hamburg, Germany}
  {Jun. 2013 - April. 2014}
  {
    \begin{cvitems}
      \item {At ABOUT YOU I took the chance to build up and lead a team of very talented developers.}
      \item {I learned how to conduct job interviews and choose the right candidate afterwards.}
    \end{cvitems}
  }
\cventry
  {Web developer}
  {NetImpact Framework GmbH (full-service web agency)}
  {Hamburg, Germany}
  {Mar. 2012 - Jun. 2013}
  {
    \begin{cvitems}
      \item {Working for a full-service web agency gained me more experiences with dealing and communicating with designers, project managers and clients than ever before.}
    \end{cvitems}
  }
\cventry
  {Web developer}
  {Creative-Task GmbH (web development agency)}
  {Frankfurt am Main, Germany}
  {Jun. 2011 - Jun. 2013}
  {
    \begin{cvitems}
      \item {My time at Creative-Task teached me how work feels from the perspection of an employee.}
      \item {I made my first steps into the creation of major web applications and.}
      \item {got to know tools for version-controlling and deployments.}
    \end{cvitems}
  }
\cventry
  {Co-Founder}
  {Toolchen GbR (web agency)}
  {Frankfurt am Main, Germany}
  {May 2008 - Dec. 2010}
  {
    \begin{cvitems}
      \item {After first experiences with minor projects I co-founded my first company in the age of 16.}
      \item {I needed to focus on school but I also wanted to push my business further. In that time I definitetely learned how to manage my time efficiently.}
    \end{cvitems}
  }

\end{cventries}
