%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
  {Project Lead, Development}
  {MamaData (Administration System for non-profit organization Sharana India)}
  {remote and Pondicherry, India}
  {Oct. 2013 - May 2014}
  {
    \begin{cvitems}
      \item {MamaData is a platform to organize and administrate sensitive data of beneficiaries, donations etc.
      }
      \item {We developed the platfrom remotely from Hamburg, Germany in a team of four developers, one designer and an overall product owner.}
      \item {At final stage we went to India for preparing the launch in-house and giving certain workshops to Sharana staff.
      }
    \end{cvitems}
  }
\cventry
  {Co-Creator}
  {solon.rocks (Web Application to democratically create music playlists online)}
  {remote}
  {Nov. 2013 - PRESENT}
  {
    \begin{cvitems}
      \item {We needed an application like this for our own purposes and so designed and developed it from scratch.}
      \item {I gained expertise in providing web socket connections for live updates and syncing many web client applications together.}
      \item {Currently there are discussions about making a startup out of solon.rocks.}
    \end{cvitems}
  }
\cventry
  {Certificate Holder}
  {Certified MongoDB Developer}
  {by MongoDB, Inc.}
  {Jun. 2013 - Aug. 2013}
  {}

\end{cventries}
